Contributions

### 2023-02-22 contributions.Rmd
same as previous but missed index and contributions pages

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# How to contribute new material to the website
If you are interested in submitting new content to the
MarineOmics.github.io website, we have a [guide](submissions_instructions.html) for you!
While the website managers will work with you to help prepare and publish your new
page, this guide can be a useful resource as you develop your content. The guide provides general instructions as well as examples of how to build specific features (eg., tables, code chunks). Prior to developing new pages, please contact the current Website Manager Jason Johns (jasonjohns[at]ucsb.edu). Do not hesitate to reach out with any other questions, comments, or features you'd like added to the guide.

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# How to contribute new material to the MarineOmics.github.io website
If you are interested in submitting new content to the
MarineOmics.github.io website, we have a [guide](submissions_instructions.html) for you!
While the website managers will work with you to help prepare and publish your new
page, this guide can be a useful resource as you develop your content. The guide provides general instructions as well as examples of how to build specific features (eg., tables, code chunks). Prior to developing new pages, please contact the current Website Manager Jason Johns (jasonjohns[at]ucsb.edu). Do not hesitate to reach out with any other questions, comments, or features you'd like added to the guide.
